TODO: A Survey of StarCraft AI Techniques

### 2012-02-27 survey.tex
adding missing sty files

\begin{abstract}
TODO: Idea of the paper is: ``one-stop guide on what is the
state of the art in Starcraft AI''. It should help people participating in the competition focus
their efforts, and also should help people implementing AI for RTS games in
general (e.g. industry).  In Gabriel's words ``RTS AI problems, Solutions, State-of-the-art, conclude on what's "solved" since \cite{Buro03rts} and what's not.''

@@

\begin{itemize}
\item Task Decomposition (or ``Architecture'')
\item Integration of Domain Knowledge
\item Reasoning with Uncertainty (including information gathering)
\item Opponent Modeling and Adaptation
\item Group and Individual Control (``micro'')
\item Planning and Resource Allocation (``macro'')
\item Spatial reasoning (``tactics'')
\end{itemize}

@@

\subsection{Micro-management}

Some interesting uses of reinforcement learning (RL) \cite{Sutton} to RTS research are in the domain of \textit{micro-management} (group and individual units control): \cite{Marthi05} employs concurrent hierarchical Q-learning (units Q-functions are combined at the group level) RL to efficiently control units in a ``one robot with multiple effectors'' fashion. \cite{Madeira06} advocates the use of prior domain knowledge to allow faster RL learning and applied their work on a turn-based strategy game. In real game setups, the actions spaces to explore is gigantic, it requires to use the structure of the game in a partial program (or a partial Markov decision process) and a shape function (or a heuristic) \cite{Marthi05}. There are other was to learn parameters of an underlying model, for instance \cite{GA} used evolutionary learning techniques, but face the same problem of dimensionality. The difficulty to work with multi-scale goals and plans is handled directly by case-based reasoning (CBR), which has been adapted for micro-management with continuous action models \cite{Molineaux08}, an integrated RL/CBR algorithm using continous models, or with hybrid CBR/RL transfer learning \cite{CBR-RL}. Reactive planning (for behavior languages) \cite{WeberCig10}, a decompositional planning similar to hierarchical task networks \cite{HTNPlanning}, allows for plans to be changed at different granularity levels and so for multi-scale (hierarchical) goals integration.

Potential fields \cite{Hagelback08,Hagelback09} are a powerful way to specify complex (with the combination of several fields, requiring a parameter-tuning method) behavior policies and are used in modern commercial games and RTS AI are using derivative of it (Supreme Commander flowfield). Self-organizing-maps (SOM) learned with evolutionary algorithms provide some way to learn (realistic) parameters for RTS units behavior \cite{teamCompositionRTS}. Bayesian programming has been applied to inverse fusion of the sensory inputs of the units \cite{SynnaeveMicroCig11}, which subsumes potential fields, allowing for integration of tactical goals directly in micro-management. There are also some cognitive approaches to RTS AI \cite{SORTS}, in which there is a human-like attention model for micro-management.

@@

Figure \ref{fig:bot-architecture} shows some representative examples of the integration architectures used by different bots in the AIIDE 2011 Starcraft AI competition \cite{???}. Each box represents an individual module with a clearly defined task (only modules with a black background can send actions directly to Starcraft). Dashed arrows represent data flow, and solid arrows represent control (when a module can command another module to perform some task). For example, we can see how SPAR is divided in two sets of modules: {\em situation analysis} and {\em decision making}, the first with three modules dedicated to analyze the current situation of the game, and the later with 4 modules dedicated to exploit that information to decide what to do. We can see how the decision making aspect of SPAR is organized hierarchically, with the higher-level module ({\em strategic decision}) issuing commands to the next module ({\em tactical decision}), which sends commands to the next module ({\em action implementation}), and so on. Only the lower-level modules can send actions directly to Starcraft.

@@

{\color{blue}
\begin{itemize}
\item Strengths and weaknesses?
\item Resource coordination in a divide-and-conquer approaches?
\item High-level strategies that do not depend on scripting? (not here, this should be discussed in Section \ref{sec:planning})
\end{itemize}
}

>>>>

\begin{abstract}
TODO: Idea of the paper is: ``one-stop guide on what is the
state of the art in Starcraft AI''. It should help people participating in the competition focus
their efforts, and also should help people implementing AI for RTS games in
general (e.g. industry).  In Gabriel's words ``RTS AI problems, Solutions, State-of-the-art, conclude on what's "solved" since (Buro 2004) and what's not.''

@@

\begin{itemize}
\item Task Decomposition (or ``Architecture'')
\item Integration of Domain Knowledge
\item Reasoning with Uncertainty (including information gathering)
\item Opponent Modeling and Adaptation
\item Group and Individual Control (``micro'')
\item Planning and Resource Allocation (``macro'')
\item Spatial reasoning
\end{itemize}

@@

@@

Figure \ref{fig:bot-architecture} shows some representative examples of the integration architectures used by different bots in the AIIDE 2011 Starcraft AI competition \cite{url1}. Each box represents an individual module with a clearly defined task (only modules with a black background can send actions directly to Starcraft). Dashed arrows represent data flow, and solid arrows represent control (when a module can command another module to perform some task). For example, we can see how SPAR is divided in two sets of modules: {\em situation analysis} and {\em decision making}, the first with three modules dedicated to analyze the current situation of the game, and the later with 4 modules dedicated to exploit that information to decide what to do. We can see how the decision making aspect of SPAR is organized hierarchically, with the higher-level module ({\em strategic decision}) issuing commands to the next module ({\em tactical decision}), which sends commands to the next module ({\em action implementation}), and so on. Only the lower-level modules can send actions directly to Starcraft.

@@

{\color{blue}
\begin{itemize}
\item Strengths and weaknesses?
\item Resource coordination in a divide-and-conquer approaches?
\item High-level strategies that do not depend on scripting? (not here, this should be discussed in Section) % \ref{sec:planning})
\end{itemize}
}
